Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-26 paper/paper.tex
Reduce todo-list, add commented-out plot statements for debugging
Mention Oriented MBR in the report
Update todo list, report updates

@@

For the purpose of this project, the OpenStreetMap road dataset has been used in the presentation of the road network around Stockholm, and in the generative process of new road networks. To assess and correct path widths and path node locations, the OpenStreetMap building footprint dataset has also been used. To make an assessment on the quality and precision of the OpenStreetMap data, the SLU map from the Swedish National Land Survey was used in comparison with the OpenStreetMap map. The SLU map conatins only building footprints and property limits. Both map segments were obtained around the Stockholm greater metropolitan area.
The exact map segments that were extracted were in both cases rectangles with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.

@@

(Fan et al., 2014) used the total building area in their reference dataset and the OpenStreetMap dataset to assess the completeness of OpenStreetMap data. The motivation for this is to eliminate semantic differences between both datasets. A very common example of a semantic error when comparing geographic data is that a large building in one dataset may be segmented into several smaller ones in the other, making one-to-one object mapping impossible. Thus using building area as an estimator for completeness solves this issue much better than i.e. the number of buildings or other objects in each dataset.
This project will use the building area in the OSM dataset versus that of the SLU dataset to determine the completeness of OpenStreetMap building data in the Stockholm area, which will then be used as an argument for how accurate the building correspondence and point proximity measures can be.

@@

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship. Footprints from different datasets may be formed at a different level of detail. Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets. To avoid this effect, key points are extracted using the Douglas-Peucker algorithm (Douglas and Peucker, 1973), to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint. The idea behind Douglas-Peucker is to recursively divide a polyline. It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$. It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$. Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded. See Algorithm 1 for a detailed view. In either case The minimum bounding rectangle (MBR) is calculated for the two polygons. Finally the MBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the MBR of the SLU building footprint. Any edges in the simplified footprints that coinside with the MBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

>>>>

\section{Related work}
Fan et al, 2015
Kunze, 2012 (reference in Fan et al)

@@

For the purpose of this project, the OpenStreetMap road dataset has been used in the presentation of the road network around Stockholm, and in the generative process of new road networks. To assess and correct path widths and path node locations, the OpenStreetMap building footprint dataset has also been used. To make an assessment on the quality and precision of the OpenStreetMap data, the SLU map from the Swedish National Land Survey was used in comparison with the OpenStreetMap map. The SLU map conatins only building footprints and property limits. Both map segments were obtained around the Stockholm greater metropolitan area.
The exact map segments that were extracted were in both cases rectangular boundaries with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.

@@

(Fan et al., 2014) used the total building area in their reference dataset and the OpenStreetMap dataset to assess the completeness of OpenStreetMap data. The motivation for this is to eliminate semantic differences between both datasets. A very common example of a semantic error when comparing geographic data is that a large building in one dataset may be segmented into several smaller ones in the other, that is to say a building in one set is represented as an aggreation of mutliple buildings in the other set. This makes one-to-one object mapping impossible. Thus using building area as an estimator for completeness solves this issue much better than i.e. the number of buildings or other objects in each dataset.
This project will use the building area in the OSM dataset versus that of the SLU dataset to determine the completeness of OpenStreetMap building data in the Stockholm area, which will then be used as an argument for how accurate the building correspondence and point proximity measures can be.

@@

TODO: Include a distribution of the shap similarity of matched building footprints, see Fan et al, page 14

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship. Footprints from different datasets may be formed at a different level of detail. Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets. To avoid this effect, key points are extracted using the Douglas-Peucker algorithm (Douglas and Peucker, 1973), to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint. The idea behind Douglas-Peucker is to recursively divide a polyline. It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$. It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$. Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded. See Algorithm 1 for a detailed view. In either case The Oriented Minimum Bounding Rectangle (MBR) is calculated for the two polygons. Finally the MBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the MBR of the SLU building footprint. Any edges in the simplified footprints that coinside with the MBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.
